There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-10 paper/icml_drau/framework.tex
Headers.
sec:continuous => sec:framework
...

\section{Near continuous time reinforcement learning}
\label{sec:continous}
% In this section, a continuous reinforcement learning framework is introduced,
% and it is shown that under this framework, the state-action value function does
% not depend on the action. We further show that in near continous domains, when
% the discretization timestep $\deltat$ is small, the difference in state-action
% value between two different actions in a fixed state is of order $\bigO(\deltat)$.
TODO. Main ideas: near continuous time environments (control, mujoco, video games, ...)
There is a time discretization $\deltat$ given by the problem. The uderlying process does not depend of $\deltat$. Need to see what is happening when changing $\deltat$. The problem is invariant to $\deltat$. The quantities we are looking at should be invariant to. The learning procedure should be invariant. Looking at the limits when $\deltat \rightarrow 0$. In simulated environments, changing $\deltat$ only means to change the FPS. In real environments, for example with robots, this could mean changing the quality of the sensors and motors.

@@

Let assume that we have a Markov Decision Process (TODO:Cite?) $\langle {\cal S}, {\cal A}, T_{\deltat}, r, \gamma\rangle$. ${\cal S}$ is the state-space, which is supposed to be continuous (TODO:not the good formulation). The action space is TODO.

We assume that the transition is continuous. This means that ... TODO. Discussion on the hypothesis, in which environments it is true. Is the condition $\forall \deltat, \forall s, \E[\|s_{k+1} - s_k \||s_k = s] \leq ?$.

>>>>

\section{Near continuous time reinforcement learning}
\label{sec:continous}
% In this section, a continuous reinforcement learning framework is introduced,
% and it is shown that under this framework, the state-action value function does
% not depend on the action. We further show that in near continous domains, when
% the discretization timestep $\deltat$ is small, the difference in state-action
% value between two different actions in a fixed state is of order $\bigO(\deltat)$.
\TODO{. Main ideas: near continuous time environments (control, mujoco, video games, ...)
There is a time discretization $\deltat$ given by the problem. The uderlying process does not depend of $\deltat$. Need to see what is happening when changing $\deltat$. The problem is invariant to $\deltat$. The quantities we are looking at should be invariant to. The learning procedure should be invariant. Looking at the limits when $\deltat \rightarrow 0$. In simulated environments, changing $\deltat$ only means to change the FPS. In real environments, for example with robots, this could mean changing the quality of the sensors and motors.}

@@

Let assume that we have a Markov Decision Process \TODO{Cite?} $\langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat, \gamma_\deltat\rangle$. ${\cal S}$ is the state-space, which is supposed to be continuous \TODO{not the good formulation}. The action space is \TODO{todo}.

We assume that the transition is continuous. This means that ... \TODO{todo}. Discussion on the hypothesis, in which environments it is true. Is the condition $\forall \deltat, \forall s, \E[\|s_{k+1} - s_k \||s_k = s] \leq ?$.

In many situations, we can assume that there is an uderlying process:
\begin{equation}
  \label{eq:diffusion}
  ds = F(s, a) + \Sigma(s, a)\dbt
\end{equation}
$F$ is the physics, and $\dbt$ is the noise.

There is convergence to the continuous process when $\deltat \rightarrow 0$.

What we want is an algorithm invariant to $\deltat$, so we need to build a discrete algorithm such that when $\deltat \rightarrow 0$, the algorithm converge to a limit algorithm doing what we want.

TODO: Explain $a_t = \pi(s_t)$ deterministic.

\subsection{Return, $\gamma$ and Value function in near continuous time}
\label{sec:ret-gamma-v}

For a continuous MDP we define the return as:
\begin{equation}
  \label{eq:continuous-return}
  R(\tau) = \int_{t=0}^\infty\gamma^tr(s_t, a_t)dt
\end{equation}

The natural discretization of this, if we want to define a discretize return $R_\delta$ for each $\deltat$ is:
\begin{equation}
  \label{eq:discretized-return}
  R_\deltat(\tau) = \sum_{k=0}^\infty\gamma^{k\deltat}r(s^\deltat_k, a^\deltat_k)\deltat
\end{equation}
